\documentclass{article}
\usepackage{bookmark}
\usepackage{calc}
\usepackage[top=0.4in,bottom=0.3in,right=0.5in,left=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{tgbonum}
\usepackage{fontawesome}

\setlist[enumerate]{topsep=0pt}
\setlist[itemize]{noitemsep,topsep=0pt}

\newlength{\remaining}
\renewcommand{\section}[1]{
  \vspace{1.0em}\setlength{\remaining}{\textwidth-\widthof{\uppercase{#1}}}
    \noindent\underline{\fontsize{10}{15}\bfseries\uppercase{#1}\hspace*{\remaining}} \\
}

\renewcommand{\subsection}[3]{
    \noindent\textbf{#1} | \emph{#2} \hfill #3  
}

\begin{document}
    \fontencoding{T1}
    \fontfamily{phv}
    \fontsize{10}{15}
    \selectfont

    \begin{center}
        \Huge\bfseries Hakancan Ozturk
    \end{center}
    
    \begin{center}
        \begin{tabular}{c c c c c}
            \href{mailto:hakancan.ozturk23@gmail.com}{\small hakancan.ozturk23@gmail.com  } $\bullet$ & 
            \href{tel:+44 7436010077}{\small +44 7436010077  } $\bullet$ & 
            \href{https://www.linkedin.com/in/hakancan}{\small \faLinkedinSquare \space linkedin/hakancan} $\bullet$ & 
            \href{https://www.github.com/hkc5} {\small \faGithub \space github/hkc5 } $\bullet$ &  
            \href{https://www.hakancanozturk.com}{\small hakancanozturk.com} \\
        \end{tabular}   
    \end{center}
    
    \vspace{-0.75em}
    

    \section{Professional Experience}
    \subsection{Software Development Engineer}{\textbf{Amazon} - London, UK}{01/2025 - Present}
    \begin{itemize}
        \item Migrating Prime Video UI elements from \textbf{React} to \textbf{SolidJS} to enhance performance, leveraging \textbf{LLM-powered automation pipelines} for efficient component refactoring and codebase optimization.
        \item Developing features for Prime Video Client Software Development Kit (SDK), enhancing streaming capabilities and user experience across multiple platforms.
    \end{itemize}

    \subsection{Machine Learning Engineer}{\textbf{Albus Technologies} - London, UK}{05/2024 - 01/2025}
    \begin{itemize}
        \item Designed a \textbf{Retrieval-Augmented Generation (RAG)} framework with context-enriched vector search, boosting retrieval relevance by 30\% compared to BM25 methods.
        \item Developed scalable real-time \textbf{Document Semantic Extraction} pipelines and \textbf{LLM agents} using \textbf{AWS} (Lambda, S3, SQS, EC2), processing millions of PDF pages and over 50K minutes of audio.
        \item Established automated \textbf{CI/CD} workflows (Docker, GitHub Actions) to deploy \textbf{FastAPI} and \textbf{Lambda} endpoints, enabling dozens of concurrent file uploads and serving over 150K customers with low-latency, robust production.
    \end{itemize}
    

    \subsection{Computing Researcher}{\textbf{Max Planck Institute} - Stuttgart, Germany}{06/2022 - 12/2022}
    \begin{itemize}
        \item Conducted \textbf{computational fluid dynamics (CFD)} simulations for biomedical micro-robots, achieving 200x efficiency gains through optimized \textbf{COMSOL simulations} in HPC environments, leading to two publications in top journals.
        \item Deployed advanced data processing pipelines using \textbf{curve fits} and \textbf{support vector machines (SVMs)} to analyze 10TB of simulation data, significantly improving predictive accuracy for robotics dynamics characterization.
    \end{itemize}


    \section{Education}
    \subsection{Imperial College London}{MSc in Applied Computational Science and Engineering}{09/2023-09/2024} \\
    Highest overall grade in class | Class representative  \hfill Distinction (78.27\%) \\
    \textit{Modules:} Machine/Deep Learning, Numerical Methods, Computational Maths, Optimization
    
    \vspace{0.25em}

    \subsection{Koc University}{BSc in Mechanical Engineering}{2020-2023} \\
    Ranked 1st in class | Graduated one year early | Merit scholarship (\$30k annually) \hfill GPA: 3.99/4.00 \\ 
    \textit{Assistant:} Introduction to Engineering - Fluid Mechanics - Numerical Methods \\
    \textit{Modules:} Propulsion Systems, Microsensors, Makerspace, Finite Element Method 


    \section{Projects}
    \subsection{MSc Dissertation: AI Surrogate Modeling for Turbulent Flow Simulations}{Imperial College London}{2024 - 2025} 
    \begin{itemize} 
        \item Discovered a novel \textbf{Grid-Invariant AI architecture} combining convolutional autoencoders and adversarial networks to simulate high-fidelity \textbf{turbulent flows}, achieving unprecedented \textbf{grid independence} and scalability.
        \item Conducted \textbf{1000+ GPU hours} of High-Performance Computing (HPC) for model optimization, enhancing \textbf{long-term stability} by 35\% and prediction accuracy by 50\%, with research leading to a forthcoming publications.
    \end{itemize}

    \subsection{Advanced Collagen Fiber Orientation Analysis}{Pekkan Biofluid Mechanics Laboratory}{2023 – 2024}
    \begin{itemize}
        \item Led advanced bio-imaging analysis using \textbf{Fast Fourier Transform (FFT)}, \textbf{Support Vector Regression (SVR)}, and \textbf{CNNs}, achieving 95\% accuracy in collagen fiber orientation prediction.
        \item Implemented a novel method leveraging \textbf{Generative Diffusion Models} in \textbf{PyTorch} for biological data augmentation, increasing dataset size by 10x while preserving accuracy.

    \end{itemize}

    
    \section{Skills \& Publications}
    \textbf{Languages \& Libraries}: Python, Javascript, C++, MATLAB, PyTorch, scikit-learn, FastAPI, React \\
    \textbf{Cloud \& DevOps}: Docker, AWS, Github Actions, HPC, Parallel Computing, High-Performance Computing
    % \textbf{Engineering Software}: COMSOL (CFD), ANSYS (Mechanics, Fluent), Siemens NX    
    
    \subsection{Publications}{2 papers with >15 citations}{}{}
    \begin{itemize}
        \item Published papers on microrobotics and ML in \textbf{Nature} Scientific Reports and \textbf{Advanced} Intelligent Systems.
        \item Preparing papers in collaboration with Max Planck Institute, BML(Koc), and ACMG(Imperial) groups.
    \end{itemize}

\end{document}
